---
title: "Lab 8: The 12 Days of Christmas"
subtitle: "Sing the Full Song"
author: "Your name"
format: 
  html:
    self-contained: true
    code-tools: true
    toc: true
    number-sections: true
editor: source
execute: 
  error: true
  echo: true
  message: false
  warning: false
---

```{r packages}
library(tidyverse)
xmas <- read.csv("https://raw.githubusercontent.com/zoerehnberg/STAT331-S23/main/practice_activities/xmas.csv")
```

[Download starter .qmd file](LA8_fprogram.qmd)

You've already created two helper functions, `pluralize_gift()` and `make_phrase()`, which you used to create a column of song phrases in the practice activity.

Today, you will write a function that sings the appropriate lines of the song for a given day. We will then use this function to iterate through the 12 days of Christmas to sing the full song!

::: callout-note
You will need to copy over your functions from the practice activity into your new lab Quarto document.
:::

```{r}
# Copy over functions from your practice activity
```

Use your PA functions to create a `Full.Phrase` column in the `xmas2` data set.

```{r}
xmas2 <- xmas |>
  mutate(
    Full.Phrase = pmap_chr(.l = list(num       = Day,
                                     item      = Gift.Item, 
                                     verb      = Verb, 
                                     adjective = Adjective, 
                                     location  = Location), 
                           .f = make_phrase))
```


## Iteration.

Write a function called `sing_day()` that takes as input:

+ A dataset (input as a dataframe).
+ A number indicating which day to sing about (input as an integer).
+ The name of a column in the dataset that contains the phrases for each day (input as a tidy name).

For example,

    sing_day(xmas2, 2, Full.Phrase)

should return

    On the second day of Christmas, my true love sent to me:
    two turtle doves and
    a partridge in a pear tree.

::: callout-tip
**Hint 1:** The `{{phrase_col}}` part, which I provided for you, lets you use column names as arguments to a function. Don't delete that line of code!

**Hint 2:** The `ordinal()` function from the **english** package could be helpful when converting the `line` input (e.g., 1) to a word (e.g., "first").
:::

```{r sing-day-function}
# Produces the string for one day of the song.
# Arguments:  dataset -- a dataframe containing information about gifts.
#             num -- the number of the day you want to sing about.
#             phrase_col -- the variable name for the column in dataset with the song phrases.
# Returns:  a string with the line of the song containing ALL gifts for the given day.

sing_day <- function(dataset, num, phrase_col){
  
  # Step 1: Setup the intro line
  # Hint: You need to convert a number (e.g., 1) to a word (e.g., first)
  num_word <- ____
  
  intro <- glue::glue("On the {num_word} day of Christmas, my true love sent to me:")
  
  # Step 2: Sing the gift phrases
  # Hint: What order are they gifts sung in each day?

    phrases <- dataset |>
      pull({{phrase_col}})

  ????
    
  ## put it together
    
  ????

}

```

::: callout-note
### A Small Test

```{r}
xmas2 |>
  sing_day(num = 2, phrase_col = Full.Phrase)
```
:::

## Use Your Functions!

Run the following code to test out your functions! The output should be the lyrics for the entire 12 Days of Christmas song.

```{r}
map_chr(1:12, ~ sing_day(dataset = xmas2, 
                         num = .x, 
                         phrase_col = Full.Phrase)) |>
  str_c(collapse = "\n") |>
  cat()
```

::: callout-warning
**You will get automatic deductions for:**

+ Functions that do not work the way they are intended.
+ Hard coding values in your in functions.
+ Not using the `map()` code supplied for you to iterate the function you just wrote.
+ Not singing the full song. Remember, each day, you get the gift for that day *and* all the prior days.
:::
