---
title: "PA 2: Using Data Visualization to Find the Penguins"
author: "NAME"
format: html
embed-resources: true
execute: 
  echo: true
  error: true
---

<!-- Insert your setup code chunk here. This is just good practice. -->

[Download the .qmd template](PA2.qmd) and save it in a reasonable location.

Today you will be exploring different types of visualizations to uncover which species of penguins reside on different islands.

Some advice:

+ **Work with those around you.**

+ If you aren't sure how to make a specific plot or how to customize a plot, look over the class text for this week and make use of the [R graphics cheatsheet](https://earobinson95.github.io/stat331-calpoly-text/02-tidy-data-and-basics-of-graphics.html#rgraphics).

+ Google is your friend! If you aren't sure how to accomplish a certain task, type what you are trying to accomplish into Google and see what other people are saying.
  + Generally, adding `ggplot` to the end of your search will help make your search results more relevant!

## Getting Started

We will be creating visualizations using the `ggplot2` package.

For this activity, we will be exploring the `penguins` data from the `palmerpenguins` package, which has [fantastic documentation with really awesome artwork](https://allisonhorst.github.io/palmerpenguins/). So, you will need to install the **palmerpenguins** package.

`install.packages("palmerpenguins")`

::: {.callout-caution}

## `install.packages()` in the console NOT in your `.qmd` file!

You should type this into your console and NOT include it in a code chunk in your `.qmd` file. Recall that we only have to install a package **once**, but load it each time we open R. Each time you *render* your `.qmd` file, **ALL**the code chunks are run. Therefore, installing a package in a code chunk would cause R to unnecessarily install the package over and over again. Not good.

:::


## Creating a Setup Code Chunk

1.  Insert a code chunk at the beginning of your document (directly under the YAML).
2.  Name the code chunk `setup`.
3.  Use the hashpipe `#|` to specify a code chunk option that prevents any messages (e.g., from loading in packages) from appearing.
4.  Load in the `tidyverse` or `ggplot2` package.
5.  Load in the `palmerpenguins` package.

::: callout-note

## Code chunk name: `setup`

Naming your code chunk "setup" has special properties in a `.qmd` - specifically, this code chunk will run automatically when you try to run a subsequent code chunk. This ensures all packages and any other specifications for your document are loaded and will not cause you errors or messages.
:::

## Dataset: `penguins`

I like to start by **seeing** the dataset I will be working with, so I am going to pull the `penguins` data into my R environment. Do you see it in the top right Environment tab?

```{r}
data(penguins)
```

6. Get to know your data. What are the variables and what units are they measured in? What does each row represent?

## Graphics

::: callout-note
Make sure to give your plots reader friendly axes labels!
:::

::: callout-note
Make sure your final report **does not** display any wanrings or messages from RStudio!
:::

7. Use <https://excalidraw.com/> (or pen and paper, a tablet, etc.) to create a **game plan** for a barchart of `species`, where `species` is mapped to the fill color of the barchart. Save or take a screenshot of your game plan -- you will be uploading this to Canvas with your practice activity submission.

8. Use `ggplot2` to create the barchart you outlined above.

```{r}

```

9. Use `ggplot2` to create a scatterplot of the relationship between the bill length (`bill_length_mm`) and bill depth (`bill_depth_mm`).

```{r}

```

10. Building on your code from (9), add an aesthetic to differentiate the species by color.

```{r}

```

11. Building on your code from (10), add the location of the penguins (`island`) to your visualization. There us more than one method to address this, however, one method will more easily address the questions below, so you might want to read those questions first!

```{r}

```

## Canvas Quiz

::: callout-tip
### Use the plots you created to answer the following questions on Canvas.

1.  Which species of penguins is represented **least** in the Palmer Penguins data set?

2.  Which species of penguins are found on **every** island?

3.  Which species of penguins are found **only** on Dream Island?

4.  Which species of penguins are found **only** on Biscoe Island?

5.  Color deficiencies can make differentiating groups difficult - which aesthetic could you add to your plot to double encode species?
:::
