---
title: "PA 5.1:  Jewel Heist"
subtitle: "Dates and Times with lubridate"
format: 
  html:
    self-contained: true
    code-tools: true
editor: source
execute: 
  error: true
  echo: true
  message: false
  warning: false
---

[Download starter qmd file](PA5_1.qmd)

```{r setup}
library(tidyverse)
library(lubridate)
```

::: callout-note
Note that the `lubridate` package is a dependency that is installed as part of the `tidyverse` package, but it is not automatically loaded.

In other words, you have already accomplished `install.packages("lubridate")` by default of installing the `tidyverse`, but you will always need to call `library(lubridate)`.
:::

## Solve the Mystery

Just down the road in Montecito, CA several rare jewels went missing last fall. The jewels were stolen and replaced with fakes, but detectives have not been able to solve the case. They are now calling in a data scientist to help parse their clues. 

A camera was located near the building where the jewels went missing, so the detectives have provided you with a list of people who may have entered the building last year. This list includes the date and time they were spotted on the camera, **in Pacific Standard Time (PST)**.

Unfortunately, the date and time of the jewel heist is not known. You have been hired to crack the case. Use the clues below to discover the thief's identity.

```{r}
# 214 total suspects
suspects <- read_csv("https://raw.githubusercontent.com/zoerehnberg/STAT331-S23/main/practice_activities/suspects.csv")
```

::: callout-note
Pay attention to the **time zone** that is assigned when the data are read in. How can you set the correct time zone?
:::

1. Based on the cleaning schedule for the room where the jewels are held, the heist was not committed in the morning.

2. The room where the heist was committed is closed on Tuesdays and Thursdays (and there were no signs of forced entry), so the heist did not happen on those days.

3. It is believed that the heist was committed within 5 weeks (35 days) of Thanksgiving 2022.

4. The detectives partially decoded a message from a notorious fence in Iceland that reminded the thief to not steal the jewels "before I'm off work for the day."

5. The thief left behind a birthday card at the scene of the crime. The date is smudged, but the day of the month is shown to be 22. It is thought that perhaps the heist took place less than three days after the thief's birthday.

6. The thief is amused by your efforts and has sent you a cryptic clue:

> "The number of seconds between midnight on Jan 1, 1970 and the time I arrived on the scene is divisible by 10."

::: callout-note
### Canvas Quiz Submission

Who is the thief? *Only one name should remain.*

:::