---
title: "PA 9.2: Mystery Animal"
subtitle: "Linear Regression"
format: 
  html:
    embed-resources: true
    code-tools: true
    toc: true
    number-sections: true
editor: source
execute: 
  error: true
  echo: true
  message: false
  warning: false
---

```{r setup}
#| include: false
library(tidyverse)
```

[Download starter .qmd file](PA9_2.qmd)

## Data

The data contain the weights of a particular animal species before and after a year of eating only roasted duck.

```{r}
mystery_animal <- read_csv("https://raw.githubusercontent.com/zoerehnberg/STAT331-S23/main/practice_activities/mystery_animal.csv")
```

## Visualize the Data

Let's start by visualizing the data. Create a scatterplot of the weights and fit a linear regression line. Make sure you use good graphic design principles in your plot!

```{r}
# Create your plot here.
```

## Linear Regression

Now let's look at the model. Fit a linear regression to determine if the Duck Diet is associated with the animal species gaining weight, losing weight, or neither.

```{r}
# Fit your linear regression model here.
```

*Based on the linear regression model, these animals tend to ____________ weight on the Duck Diet.*

## Residuals

Finally, let's look at model fit. Extract the residuals *(observed value minus predicted value)* of your linear model. Plot the residuals versus `weight_before`.

::: callout-tip

There are a few different ways to obtain your residuals. My favorite is the `augment()` function from the `broom` package. I like this option because it gives you all of the information from your linear regression in a tidy *tibble*!

:::

```{r}
# Extract and plot the residuals here.
```

## Canvas Submission: Mystery Animal

> What animal do you see in the residual plot?
