---
title: "Challenge 9: Formatting Nice Tables"
format: 
  html:
    self-contained: true
    code-tools: true
    toc: true
    number-sections: true
editor: source
execute: 
  error: true
  echo: true
  message: false
  warning: false
---

```{r setup}
#| include: false
library(tidyverse)
```

For this Challenge you will explore how to generate nice looking tables for HTML documents. There are many packages for generating tables, but I prefer the `kable()` function from the `knitr` package for *simple* tables and the `datatable()` function from the `DT` package for *more sophisticated* tables.

I want you to think of tables just like the visualizations you've been making. **We want all aspects of our tables to be clear to the reader.** Tables are also a great avenue to display creativity! In fact, there is a yearly [Posit table contest](https://www.rstudio.com/blog/rstudio-table-contest-2022/), and [here](https://community.rstudio.com/c/table-gallery/64) is a gallery of the award winning tables.

## Formatting Basic Tables

Use the `kable()` function from the [kable package](https://bookdown.org/yihui/rmarkdown-cookbook/kable.html) to create a nice, basic HTML version of the tables in both **Q1** and **Q12** in Lab 9.

::: callout-warning
Similar to axis labels in visualizations, **every** column name in a table should describe what it contains. For example, a column of `n` is less explanatory than `Frequency of Babies`.
:::

```{r}
# Code for Q1
```

## Formatting Nicer Tables

There are two options for creating nicer tables:

  + [kableExtra package](https://bookdown.org/yihui/rmarkdown-cookbook/kableextra.html)
  + [DT package](https://rstudio.github.io/DT/).
  
Use either the `DT` or `kableExtra` packages to spice up **both** your tables. You should add different features to the two tables.

Some ideas on how to "spice up" a table:

+ Change the font and / or font size.
+ Add striping and / or cell borders.
+ Create custom formatting of columns.
+ Allow the user to interact with the table (e.g., filtering columns, editing cells).
    
```{r}
# Code for Q2
```
